---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickplot

<!-- badges: start -->
<!-- badges: end -->

The purpose of quickplot is to produce `ggplot` in a more convenient way. It can make a beautiful ggplot using a single function.

## Installation

You can install the released version of quickplot from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("quickplot")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Yifan-Yin/quickplot")
```
## Basic Usage
Make a boxplot to visualize the distribution of life Expectancy in different different continents by using the `ggboxplot()` function. 
```{r example}
library(quickplot)
library(gapminder)
## use ggboxplot to make a boxplot
ggboxplot(gapminder, categorical_variable = 'continent', numeric_variable = 'lifeExp')
```

